---
title: "knit literal knitr chunks"
author: "Thell"
date: "03/23/2014"
output:
  html_document:
    highlight: pygments
    self_contained: yes
    toc: yes
  pdf_document:
    toc: yes
---

```{r "knitr-setup", include=FALSE, cache=FALSE}
# knitr-setup should be the first chunk in the document.
knitLiteral::kast_on()
```

About
========================

The knitLiteral package gives authors the ability to easily output
the exact the source of a chunk without side-effects. It is simple
to use; just remember that knitr processes chunk options as they occur
and options can occur more than once.

The main option that knitLiteral allows is `literal=TRUE`. This
option allows you to generate the output you literally want to use
in knitr to produce a result _without_ repeating yourself or
breaking the parser. (_Notice the use of 4 backticks instead of
the minimal 3 to allow R syntax highlighting to work._)

If the _literal_ label is used more than once in a particular chunk
and the options __end__ with `literal=TRUE` then only the final
`literal=TRUE` will be removed, which allows for illustrating how
the literal chunk was produced.

Hook Setup
========================

It is very easy to initialize using `kast_on` in your first chunk.

````{r "knitr-setup", include=FALSE, cache=FALSE, literal=TRUE, include=TRUE, echo=FALSE, results='asis'}
````

It is very easy to style using `dye` in your closing chunk.

````{r "include-after", echo=FALSE, results='asis', opts.label="literal"}
# include-after should be the last chunk in the document.
knitLiteral::dye()
````


Examples
========================

## Basic

All of the _Basic_ examples are achieved by simply adding the
`literal=TRUE` option at the end of a normal chunk.

### No output, caching only.

This sets up the `example` chunk for later reuse.

````{r "example", eval=FALSE, echo=FALSE, literal=TRUE}
print('hello world!')
print('hello again!')
````

### Default usage.

````{r "example", literal=TRUE}
````

#### Global default comment set to NA:

Set the global default for the `comment` param to more closely match
console output using `opts_chunk$set(comment=NA)`
`r knitr::opts_chunk$set(comment=NA)`

````{r "example", literal=TRUE}
````

#### Override a global default comment:

````{r "example", comment="override > ", literal=TRUE}
````


### Output combinations

#### No echo:

````{r "example", echo=FALSE, literal=TRUE}
````

#### Collapsed:

````{r "example", collapse=TRUE, literal=TRUE}
````

#### Held:

````{r "example", results='hold', literal=TRUE}
````

#### Collapsed & held:

````{r "example", collapse=TRUE, results='hold', literal=TRUE}
````

## Intermediate

### Echo with no-eval followed by no-echo held results:

The next two chunks are shown as _literal_ _literal_ chunks to
illustrate what can be done to achieve particular results.

````{r "example", eval=FALSE, literal=TRUE, echo=FALSE, opts.label="literal-reuse", indent="> "}
````
````{r "example", echo=FALSE, results='hold', opts.label="literal-reuse", literal=TRUE, indent="> "}
````

````{r "example", eval=FALSE, literal=TRUE, echo=FALSE}
````
````{r "example", echo=FALSE, results='hold', opts.label="literal-reuse"}
````

````{r "example", eval=FALSE}
````
````{r "example", echo=FALSE, results='hold'}
````

### Echo with no-eval followed by no-echo and collapsed results:

````{r "example", eval=FALSE, literal=TRUE, echo=FALSE, opts.label="literal-reuse", indent="> "}
````
````{r "example", echo=FALSE, collapse=TRUE, opts.label="literal-reuse", literal=TRUE, indent="> "}
````

````{r "example", eval=FALSE, literal=TRUE, echo=FALSE}
````
````{r "example", echo=FALSE, collapse=TRUE, opts.label="literal-reuse"}
````

````{r "example", eval=FALSE}
````
```{r "example", echo=FALSE, collapse=TRUE}
```

## Advanced

### Silent Tidy of training chunk.

Imagine having a chunk to use for training, but it needs tidying,
and the tidying has nothing to do with the training. By taking
advantage of how knitr handles chunk options a chunk can be
silently turned into a nice example.

1.  Starting with a cached chunk like this

````{r "tidy-example", echo=FALSE, eval=FALSE, literal=TRUE}
# This should not be displayed, it is just a note to myself

# that this coding is horrible and would be _wrong_.

##' Without a doubt!

if ( ( knitr::opts_current$get("literal") == TRUE ) && ( knitr::opts_current$get("literal") == TRUE ) )
  {
  foo<-FALSE } else {
    foo = TRUE
  listfoo <- list( first="second", second="third", third="fourth", fourth=fifth, and="so on")
}
````

2.  Then making a new knitr options template

````{r "opt_template", include=FALSE, cache=FALSE, literal=TRUE, include=TRUE, echo=FALSE}
knitr::opts_template$set( "literal-tidy"=
  list( literal=TRUE, echo=FALSE, eval=FALSE, tidy=TRUE,
        tidy.opts=c( width.cutoff=50, keep.comment=FALSE,
                     keep.blank.line=FALSE, replace.assign=TRUE)))
````

3.  And using it like this

````{r "tidy-example", opts.label="literal-tidy", literal=TRUE, literal.opts=list(empty=TRUE)}
````

4.  Results in

````{r "tidy-example", echo=FALSE, eval=FALSE, literal=TRUE, tidy=TRUE, tidy.opts=c("width.cutoff"=50, "keep.comment"=FALSE, "keep.blank.line"=FALSE, "replace.assign"=TRUE)}
````

A much better, although still bad, example.

******

# The pandoc markdown output.

Typing this in the rmarkdown (`.Rmd`)

````{r "example", eval=FALSE, literal=TRUE, echo=FALSE, opts.label="literal-reuse"}
````
````{r "example", echo=FALSE, collapse=TRUE, opts.label="literal-reuse", opts.label="literal-reuse"}
````
````{r "example", eval=FALSE, opts.label="literal-reuse"}
````
````{r "example", echo=FALSE, collapse=TRUE, opts.label="literal-reuse"}
````

yields this clearly indicated, clean markdown (`.md`) showing what to type for the
markdown chunks, and what the results would be.

    ````{r "example", eval=FALSE, literal=TRUE, echo=FALSE}
    ````
    ````{r "example", echo=FALSE, collapse=TRUE, opts.label="literal-reuse"}
    ````
    ````{r "example", eval=FALSE}
    ````
    ````{r "example", echo=FALSE, collapse=TRUE}
    ````

# Styling Information

## HTML Class Information.

The knitr chunk `pre class` and `code class`.

~~~~~~~~~~~{.html}
<pre class="sourceCode knitr r markdown"><code class="sourceCode r">
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

## CSS

The style for the knitr blocks was accomplished by simply using four
back ticks instead of three so the R syntax highlighter would work
and by defining a style.

~~~~~~ {.css}
````{r "literalize.css", echo=FALSE, results='asis'}
css <- system.file("css/literalize.css", package = "knitLiteral")
css <- readLines(css)
cat( css, sep="\n" )
````
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

## Javascript for rmarkdown v1

~~~~~~ {.javascript}
````{r "literalize.js", echo=FALSE, results='asis'}
js <- system.file("js/literalize.js", package = "knitLiteral")
js <- readLines(js)
cat( js, sep="\n" )
````
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

````{r "include-after", echo=FALSE, results='asis'}
````
